% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2023 Corben Dredge <cdredge@protonmail.ch> https://corbenshiro.github.io

% This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.
\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
% Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
% Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{{\Large Corben Dredge}} \\
\texttt{cdredge@protonmail.ch} & \texttt{https://github.com/corbenshiro} \\
\texttt{+44 7*********} & References are available upon request.

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{FORMAL EDUCATION}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Newham Sixth Form College}{}{Computer Science}{September 2018 - July 2019}
	\begin{itemize}
		\resitem{Pearson BTEC Level 3 90-credit Diploma in Information Technology}
	\end{itemize}

\item
	\ressubheading{Newham Sixth Form College}{}{Networking and Systems}{September 2017 - July 2018}
	\begin{itemize}
		\resitem{Pearson BTEC Level 2 First Extended Certificate in Information and Creative Technology}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{WORK EXPERIENCE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Red Hat, Inc.}{}{Software Engineer, Intern}{May - August 2019}
	\begin{itemize}
		\resitem{Worked on RPM packaging through spec file engineering.}
		\resitem{Bootstrapped (via Podman) containerized Apache Maven and Gradle environments with the Supersonic Subatomic Java framework known as Quarkus.}
		\resitem{Tinkered with Unix-like systems such as GNU/Linux (various distributions; Fedora, Debian, etc.), Alpine Linux (OpenRC with BusyBox compiled against musl libc) and BSD derivatives.}
	\end{itemize}

\item
	\ressubheading{Newham Sixth Form College}{}{IT Staff Assistant, Intern}{December 2017}
	\begin{itemize}
		\resitem{Rebuilt workstations and flashed its storage drives with operating system disk images (mainly Windows 7 Professional and Windows 10 Education editions) for later use within the college.}
		\resitem{Fixed printing errors via reloading the printers\textquotesingle{} respective daemons.}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{AUTHORED PROJECTS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Blog:} General-purpose blog with a slant towards technology. Other topics will be covered. \texttt{https://corbenshiro.github.io/}

\item {\bf Security Article:} Comprehensive information regarding how I secure my website, webpages and documents (including this curriculum vitæ). \texttt{https://corbenshiro.github.io/security/}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{TECHNICAL SKILLS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Operating Systems:} NixOS, Fedora, Debian, OpenBSD, FreeBSD, Sculpt, Windows 10 Enterprise

\item {\bf Programming Languages:} Nix, C, Lua, Go, Python

\item {\bf Kernel \& Application Security:} grsecurity, PaX, Capsicum, Genode OS Framework

\item {\bf STIGs:} Windows 10 V2R2, Oracle JRE 8 V1R5

\item {\bf Cryptography:} Ed25519 (SHA-512, Curve25519)

\item {\bf Unix Shells:} Bourne-Again shell (bash), Bourne shell (sh), Almquist shell (ash, sh), Public domain KornShell (pdksh)

\item {\bf Revision Control Systems:} Git, Mercurial (hg), CVS

\item {\bf Typesetting:} \TeX, \LaTeX

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{HOBBIES \& INTERESTS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item {\bf Tabletop RPGs:} AD\&D 2E, GURPS 4E, Pathfinder 2E

\item {\bf MUDs:} MudCore, Evennia

\item {\bf Sports \& Fitness:} Keepie uppie (football kick-ups), weightlifting

\item {\bf Animation:} Pangu, Douluo Dalu, Record of Lodoss War, Vampire Hunter D: Bloodlust

\item {\bf Comic Books:} All-Star Superman, Devilman, Bastard!!, Solo Leveling

\end{itemize}

\end{document}
